---
title: "Getting Started with MFA Package"
author: "Saurabh Belsare, Ankush Desai, Jieun Kim and Allen Tang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(mfa)
```

## Multi-Factor Analysis

The package `"mfa"` implements a statistical multivariate technique called Multiple Factor Analysis (MFA) and visualizes the compromise of the tables, partial factor scores, and variable loadings of given dimensions (i.e., components). Additionally, this package provides a set of complementary functions and methods for: (1) summaries of eigenvalues, (2) contributions (by observations, variables, and tables, respectively), (3) $R_V$ and $L_g$ coefficients, and (4) bootstrapping. 

## Creating a `mfa`

The first step is to create a `"mfa"` object with the function `mfa()`:

```{r}
mymfa <- mfa()
mymfa
```

By default, `mfa()` creates an object with pre-processed matrix by centering and normalizing each column such that its mean is equal to 0 and the sum of the square values of all its elements is equal to 1. You can change the defaults with arguments `center` and `scale`:

```{r}
not_centered <- mfa(..., center = FALSE)
not_normalized <- mfa(..., scale = FALSE)
```

## Visualizing 

You can use the function `plot()` to create a graphic with
```{r, fig.show='hold'}
plot(mymfa)
```




